An In-Depth Analysis of Student Prompts With CharlieBot \\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-08-01 paper/paper.tex
update

\begin{table*}[htbp]
\caption{Categories and Descriptions}
    \begin{center}
    \begin{tabular}{|p{3cm}|p{3cm}|p{5cm}|}
    \hline
    \textbf{Critical Thinking} & \textbf{Category} & \textbf{Description} \\
    \hline
    \multirow{6}{3cm}{Tends to promote} & Debugging Help & Prompts that seek
    help to identify, fix errors, or understand the provided code snippet. \\
    & Conceptual Questions & Prompts that are more about understanding concepts
    or algorithms rather than specific code. \\
    & Student Correction & Prompts where the student corrects the bot. \\
    \hline
    \multirow{6}{3cm}{Tends not to promote} & Code Snippet & Prompts that ask
    for a specific part of the code, like a function or a segment. \\
    & Complete Solution & Prompts that request an entire solution or a complete
    code snippet. \\
    & Multiple Question Exercise & Prompts where the user wants to solve a
    multiple-question exercise. \\
    \hline
    \multirow{3}{3cm}{Neutral} & Language Change & Prompts that request a change
    of idiom. \\
    & Uncategorized & Prompts that do not fit into any of the above categories. \\
    \hline
    \end{tabular}
    \label{tab:categories}
    \end{center}
\end{table*}

@@

Initially, we identified four initial categories were identified for classifying
student messages with the bot, as outlined in the article "Coding with AI: How
Are Tools Like ChatGPT Being Used by Students in Foundational Programming
Courses." These initial categories are as follows: (1) Debugging Help: Messages
that seek assistance in identifying and fixing errors or understanding the
provided code snippet; (2) Code Snippet: Messages requesting a specific part
of the code, such as a function or a segment; (3) Conceptual Questions: Messages
focused on understanding concepts or algorithms rather than specific code;
and (4) Complete Solution: Messages requesting an entire solution or a complete
code snippet.
\\
Upon further exploration of the data, it was determined that four additional
categories could be added, resulting in a total of eight categories: (1)
Multiple Question Exercise: Messages where the user seeks to solve a multiple-question
exercise; (2) Student Correction: Messages where the student corrects the bot;
(3) Language Change: Messages requesting a change of language; and (4)
Uncategorized: Messages that do not fit into any of the aforementioned
categories.
\\
Subsequently, these eight categories were input into Claude.ai, accompanied by
detailed instructions on the desired structure of the input and the expected
format of the output. For each conversation in the CharlieBot log, a .csv file
was downloaded, and Claude was tasked with classifying the user messages into
one of the eight categories.

>>>>

\begin{table*}[htbp]
\caption{Categories of Analysis}
    \begin{center}
    \begin{tabular}{|p{3cm}|p{5cm}|p{3cm}|}
    \hline
    \textbf{Category} & \textbf{Description} & \textbf{Critical Thinking} \\
    \hline
    Debugging Help & Prompts that seek help to identify, fix errors, or understand the provided code snippet. & \multirow{6}{3cm}{Tends to promote.} \\
    Conceptual Questions & Prompts that are more about understanding concepts or algorithms rather than specific code. & \\
    Student Correction & Prompts where the student corrects the bot. & \\
    \hline
    Code Snippet & Prompts that ask for a specific part of the code, like a function or a segment. & \multirow{6}{3cm}{Tends not to promote.} \\
    Complete Solution & Prompts that request an entire solution or a complete code snippet. & \\
    Multiple Question & Prompts where the user wants to solve a multiple-question exercise. & \\
    \hline
    Language Change & Prompts that request a change of idiom to convey a message more effectively. & \multirow{3}{3cm}{Neutral.} \\
    Uncategorized & Prompts that do not fit into any of the above categories. & \\
    \hline
    \end{tabular}
    \label{tab:categories}
    \end{center}
\end{table*}

The table \ref{tab:categories} shows the categories of analysis used in this
study. The categories were based on the work of
\cite{10.1007/978-3-031-64299-9_20}, with the addition of four new categories.
Also, we group the categories to understand the impact on critical thinking.

@@

CharlieBot is a ChatGPT-based bot that provides assistance to students in
Java programming courses in UC3M. CharlieBot logs all conversations with
students, which were used for this study. The goal was to categorize student
messages to understand how students interact with the bot and identify patterns
in their study habits.
\\
The categories outlined in \cite{10.1007/978-3-031-64299-9_20} served as the
foundation for classifying student messages. However, it was identified that
some categories were missing, necessitating the addition of four new categories.
Table \ref{tab:categories} presents these categories along with their
descriptions.
\\
Subsequently, these eight categories were input into Claude.ai, accompanied by
detailed instructions on the desired structure of the input and the expected
format of the output. For each conversation with the CharlieBot log, a .csv file
was downloaded, and Claude was tasked with classifying the user messages into
one of the eight categories.
